Precise predictions for same-sign W-boson scattering at the LHC

### 2018-03-14 Draft/article.tex
Minor typos in acknowledgment fixed

The authors are grateful to the members of the VBSCan collaboration for several discussions and comments to this work. The author also thank
the {\sc Pythia8} developers, in particular Stefan Prestel, Torbjorn Sjostrand and Peter Skands for 
discussions and clarifications about the third-jet rapidity spectrum. MZ would like to talk Andreas Papaefstathiou, Christian Reuschle and David Grellscheid 
for their help with {\sc Herwig7}. RF, HSS and MZ thank the {\sc MadGraph5\_aMC@NLO} authors for discussions, and
they are particularly grateful to Valentin Hirschi for comments to this manuscript.

>>>>

The authors are grateful to the members of the VBSCan collaboration for several discussions and comments to this work. The author also thank
the {\sc Pythia8} developers, in particular Stefan Prestel, Torbjorn Sjostrand, and Peter Skands for 
discussions and clarifications about the third-jet rapidity spectrum. RF, HSS, and MZ thank the {\sc MadGraph5\_aMC@NLO} authors for discussions, and
they are particularly grateful to Valentin Hirschi for comments on the manuscript.
